---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SCTORvalidation

<!-- badges: start -->

`r badger::badge_custom("dev version", as.character(packageVersion("SCTORvalidation")), "blue", "https://github.com/SwissClinicalTrialOrganisation/SCTORvalidation_Rpackage")`

<!-- badges: end -->

The goal of SCTORvalidation is to provide an easy approach for the documentation and implementation of package and function tests for the SCTO R validation project. Package validations themselves can be found in the [validation_platform repository](https://github.com/SwissClinicalTrialOrganisation/validation_platform).

## Installation

You can install the development version of validation from [GitHub](https://github.com/SwissClinicalTrialOrganisation/SCTORvalidation_Rpackage) with:

``` r
# install.packages("devtools")
devtools::install_github("SwissClinicalTrialOrganisation/SCTORvalidation_Rpackage")
```

or

``` r
install.packages('SCTORvalidation', repos = c('https://ctu-bern.r-universe.dev', 'https://cloud.r-project.org'))
```

## Testing

The package contains a `test` function which is used to run all tests for a named package.

```{r example, eval=FALSE}
library(SCTORvalidation)
## basic example code

# test("presize")
```

<!-- The output of this function is a string which can be copied and pasted into an appropriate issue on the GitHub `pkg_validation` repository. -->


### Implementing new tests

All tests are stored in the [`validation_tests` repository](https://github.com/SwissClinicalTrialOrganisation/validation_tests) in package specific folders. E.g. the `tests/presize` folder contains tests relevant to the `presize` package.

(At least) three files are required. The test_skeleton function can be used to create these files.

1. setup-`package`.R
2. info.txt 
3. test-`function`.R

The `setup-package.R` file installs, updates and/or loads the package being tested and any other relevant steps (e.g. loading a dataset).

`info.txt` contains a plain text description of the tests.

test-`function`.R contains the tests themselves. Tests should be written using `testthat` syntax, e.g.

```
test_that("'1:3' creates a sequence of 1, 2, 3", 
          expect_equal(1:3, c(1,2,3)))
```

### Checking your session

```{r}
library(dplyr)
library(lubridate)

SCTORvalidation::check_session()
```

